Predictive Quantization for MIMO-OFDM SVD Precoders using Reservoir Computing Framework

### 2019-04-18 paper/main.tex
Minor fixes

\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||W_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2

@@

W_{i,t}^{\text{out}}\gets\text{argmin}_{W_{i,t}^{\text{out}}}(\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||W_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)

@@

Computing the gradients $\frac{\partial \mathcal{O}_t}{\partial W_{i,t}^{\text{out}}}$ and setting it to null gives,

@@

W_{i,t}^{\text{out}}=\frac{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})}{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2}

@@

where $\texttt{outer}(\bx,\by)$ is the outer product between $N_x$ dimensional vector $\bx$ and $N_y$ dimensional vector $\by$ to give a $N_x\times N_y$ matrix. Let $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})$ be $\text{num}_{i,t}$ and $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2$ be $\text{den}_{i,t}$, with $W_{i,t}^{\text{out}}=\frac{\text{num}_{i,t}}{\text{den}_{i,t}}$. Observe that,

@@

W_{i,t}^{\text{out}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\tilde{\bu}_{i,t},\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}

@@

We just need to store the matrix $\text{num}_{i,t-1}$, a number $\text{den}_{i,t-1}$, and using the current reservoir state $\br_{i,t}$ and obtained $\tilde{\bu}_{i,t}$ from \eqref{fpqp}, one can calculate $W_{i,t}^{\text{out}}$ for forward calculation of $\tilde{\bu}_{i,t+1}$.

@@

To conclude this section, now summarize and touch upon the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
The first key advantage of the proposed framework, over the past work in this line \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
To support the above statement, observe \eqref{res_upd},\eqref{fpqp} to obtain $\bW^{\text{out}}_{i,t}$ from $\tilde{\bu}_{i,t}$, and \eqref{fwd_pred} to obtain $\bP_{i,t+1}$ combinedly,
\begin{equation*}
\highlight{W_{i,t}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bu}_{i,t-1}),\text{fb}_{i,t}),\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
\end{equation*}
\begin{equation*}
\highlight{\bP_{i,t+1}}=f_P(\tilde{\bU}_{i,t})=\highlight{\bW^{\text{out}}_{i,t}}\text{tanh}(\bA_i\br_{i,t}+\bW^{\text{in}}_i\highlight{\tilde{\bu}_{i,t}})
\end{equation*}
The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass of the framework ensures that prediction function `'learns' the correlations brought about by $q_P$, in addition to temporal correlations. %Better framing possible
This is done by optimizing $W_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_t$).
The updated $W_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_t$.

>>>>

\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bp_{i,t}-\tilde{\bu}_{i,t}||^2=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2

@@

\bW_{i,t}^{\text{out}}\gets\text{argmin}_{\bW_{i,t}^{\text{out}}}(\mathcal{O}_t=\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\bW_{i,t}^{\text{out}}\br_{i,t}-\tilde{\bu}_{i,t}||^2)

@@

Computing the gradients $\frac{\partial \mathcal{O}_t}{\partial \bW_{i,t}^{\text{out}}}$ and setting it to null gives,

@@

\bW_{i,t}^{\text{out}}=\frac{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})}{\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2}

@@

where $\texttt{outer}(\bx,\by)$ is the outer product between $N_x$ dimensional vector $\bx$ and $N_y$ dimensional vector $\by$ to give a $N_x\times N_y$ matrix. Let $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}\texttt{outer}(\tilde{\bu}_{i,s},\br_{i,s})$ be $\text{num}_{i,t}$ and $\sum_{s=1}^{t}\frac{1}{\lambda^{t-s}}||\br_{i,s}||^2$ be $\text{den}_{i,t}$, with $\bW_{i,t}^{\text{out}}=\frac{\text{num}_{i,t}}{\text{den}_{i,t}}$. Observe that,

@@

\bW_{i,t}^{\text{out}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\tilde{\bu}_{i,t},\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}

@@

We just need to store the matrix $\text{num}_{i,t-1}$, a number $\text{den}_{i,t-1}$, and using the current reservoir state $\br_{i,t}$ and obtained $\tilde{\bu}_{i,t}$ from \eqref{fpqp}, one can calculate $\bW_{i,t}^{\text{out}}$ for forward calculation of $\tilde{\bu}_{i,t+1}$.

@@

To conclude this section, now summarize and touch upon the novel points of the reservoir computing based framework proposed for predictive quantization of SVD precoding.
The first key advantage of the proposed framework, over the past work in this line \cite{Gupt1905:Predictive,6891198,6545375} is that the prediction function and quantization function are not independent of each other.
To support the above statement, observe \eqref{res_upd},\eqref{fpqp} to obtain $\bW^{\text{out}}_{i,t}$ from $\tilde{\bu}_{i,t}$, and \eqref{fwd_pred} to obtain $\bP_{i,t+1}$ combinedly,
\begin{equation*}
\highlight{\bW_{i,t}^{\text{out}}}=\frac{\frac{\text{num}_{i,t-1}}{\lambda}+\texttt{outer}(\highlight{q_P}(f_P(\tilde{\bu}_{i,t-1}),\text{fb}_{i,t}),\br_{i,t})}{\frac{\text{den}_{i,t-1}}{\lambda}+||\br_{i,t}||^2}
\end{equation*}
\begin{equation*}
\highlight{\bP_{i,t+1}}=f_P(\tilde{\bU}_{i,t})=\highlight{\bW^{\text{out}}_{i,t}}\text{tanh}(\bA_i\br_{i,t}+\bW^{\text{in}}_i\highlight{\tilde{\bu}_{i,t}})
\end{equation*}
The dependence between $f_P$ and $q_P$ in our framework is in the sense that the backward pass of the framework ensures that prediction function `'learns' the correlations brought about by $q_P$, in addition to temporal correlations. %Better framing possible
This is done by optimizing $\bW_{i,t}^{\text{out}}$ such that the prediction output to be as close to the output from $q_P$ (Objective function $\mathcal{O}_t$).
The updated $\bW_{i,t}^{\text{out}}$ is then used in forward pass to predict $\bP_{i,t+1}$, which is hopefully closer to $\tilde{\bU}_{i,t+1}$ than $\bP_{i,t}$ was to $\tilde{\bU}_{i,t}$ due to optimization of $\mathcal{O}_t$.
